### 2017-07-04 README.Rmd
cutting down the package to minimal features for CRAN 0.1.0
move readme figures into man/

---
output:
  md_document:
    variant: markdown_github
---

@@

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-figs/README-"
)

@@

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->
[![Travis-CI Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/visdat/master.svg)](https://codecov.io/github/njtierney/visdat?branch=master)

@@

There are also experimental functions, which include guessing values,  comparing two dataframes, and adding interactivity. These are described in detail in the vignette ["Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).

@@

vis_dat(typical_larger_data)

>>>>

---
output: github_document
---

@@

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

@@

<!-- add a TravisCI badge -->
<!-- Add an appVeyor badge -->

[![Travis Build Status](https://travis-ci.org/njtierney/visdat.svg?branch=master)](https://travis-ci.org/njtierney/visdat)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/njtierney/visdat?branch=master&svg=true)](https://ci.appveyor.com/project/njtierney/visdat)[![Coverage Status](https://img.shields.io/codecov/c/github/njtierney/visdat/master.svg)](https://codecov.io/github/njtierney/visdat?branch=master)

@@

@@

vis_dat(typical_data_large)
